Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Quasiperiodic Variables from TESS

### 2023-08-13 paper/ms.tex
update ms

The CQV light curves cannot be explained by pure starspots.  Although
all young M dwarfs are spotted, this tends to produce flux variations
over characteristic timescales of the rotation period, $P_{\rm rot}$,
and its half-harmonic, $0.5\,P_{\rm rot}$.  If one fine-tunes the
viewing geometry, starspots can produce dips with durations as short
as $\approx$$0.2\,P_{\rm rot}$, and the dip amplitudes quickly
decrease due to limb-darkening (see \citealt{2017AJ....153..152S},
Figures 37-41).  The observed dips in CQVs can happen over durations as
short as $0.05\,P_{\rm rot}$ with characteristic depths of a few
percent; a ``starspot-only'' scenario can be discarded for any object
with dips that are sufficiently deep and short in duration
\citep{2017AJ....153..152S,2021MNRAS.500.1366K}.   The timescales and
amplitudes of the flux variations in such objects instead require
sharp geometries with material extrinsic to the stellar surface
\citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  Since the
entire class of star is probably part of the same phenomenon, we
therefore discard the ``spot-only'' scenario.

A few competing explanations for what causes the complex quasiperiodic
variability are shown in Figure~\ref{fig:f1}.  The ``clump'' scenario
invokes opaque dust clumps orbiting near the Keplerian corotation
radius, which periodically eclipse the star
\citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  The ``prominence''
scenario invokes long-lived condensations of cool and dense
marginally-ionized gas, embedded within the hotter corona, that would
be centrifugally supported near corotation
\citep{1989MNRAS.238..657C,2019MNRAS.482.2853J,2022MNRAS.514.5465W}.
Such structures are analogous to quiescent prominences and filaments
seen in the solar corona \citep[see e.g.][]{2015ASSL..415.....V},
though at much larger relative distances from the stellar surface.  A
final possibility that has been suggested is one of a ``screen'', in
which the inner wall of a quiescent circumstellar disk blocks a
portion of the stellar surface to produce sudden dips whenever spots
come into view \citep{2019ApJ...876..127Z}.

The dust clump and prominence hypotheses seem most plausible.  They
are qualitatively similar, except that one invokes opacity from dust,
while the other invokes opacity from gas, likely bound-free
transitions in hydrogen or perhaps a molecular opacity.  The screen
scenario seems inconsistent with the degree of observed periodicity,
the lack of infrared excess, and the observed lifetime of CQVs
extending an order of magnitude longer than the $\approx$$10^7$ year
timescale often quoted for primordial disk dispersal.  However,
unambiguous evidence in support of any one scenario has yet to be
acquired.  Such evidence might include a spectroscopic detection of
silicate 10\,$\mu$m dust absorption during a dip, or perhaps detection
of transient Balmer-line excesses as a function of cycle phase,
similar to observations made in systems such as AB~Dor
\citep[see][]{1999ASPC..158..146C} or PTFO 8-8695
\citep{2016ApJ...830...15J}.

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.96\textwidth]{annotated_lp12502.pdf}
		\vspace{-0.3cm}
		\caption{
			{\bf Validation plots used to  label CQVs}.  The complete figure
			set, with one image per sector for each of \ncpvsfound\ CQVs
			and CQV candidates
			is available online {\bf For internal collaboration review:
				\url{https://www.dropbox.com/scl/fo/zlj3txot4cvymfb22wewu/h?dl=0&rlkey=3ec5f9o5xewrixzfkhkdenopa}}.
			Panels are as follows.
			{\it a)}: Phase-folded light curve; gray points are raw 2-minute
			data and black points are binned to 200 points per cycle.
			{\it b)}: Phase-dispersion minimization (PDM) periodogram.
			Dotted lines show up to the 10$^{\rm th}$ harmonic and
			subharmonic.
			{\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
			circles displayed for scale.
			{\it d)}: Cleaned light curve, binned to 20-minute cadence, in
			Barycentric TESS Julian Date (BTJD).
			{\it e)}: Phase-folded light curve, binned to 100 points per
			cycle.  The gray line denotes the automated spline-fit to the
			wrapped phase-folded light curve, and small gray triangles
			denote automatically identified local minima.
			{\it f)}: Phase-folded light curve at twice the peak period.
			{\it g)}: Phase-folded light curve at half the peak period.
			{\it h)}: Phase-folded time-series within the ``background''
			aperture defined in the SPOC light curves.
			{\it i)}: Phase-folded flux-weighted centroid in the column
			direction.
			{\it j)}: Phase-folded flux-weighted centroid in the row
			direction.
			{\it k)}: Gaia DR2 color--absolute magnitude diagram.     
			The gray background denotes stars within 100\,pc.
			{\it l)}: Information from Gaia DR2, TIC8, and the automated
			dip-counting search pipeline.  ``Neighbors'', abbreviated
			``nbhr'', are listed within apparent distances of 2 TESS pixels
			if $\Delta T$$<$2.5.
			{\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities, calculated
			using positions, proper motions, and the parallax.
		}
		\label{fig:vet}
	\end{center}
\end{figure*}

@@

The mosaic in Figure~\ref{fig:cqvs} shows phased light curves for the
\ngoods\ CQVs.  The objects are sorted first in order of the number of
TESS 120-second cadence sectors in which they clearly demonstrated the
CQV phenomenon, and secondarily by descending brightness.  The top
five objects by this metric are TIC~300651846 ($T$$=$13.5, 12
sectors); TIC~402980664 ($T$$=$11.1, 7 sectors); TIC~89463560
($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5 sectors); and
TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest five CQVs span
9.3$<$$T$$<$11.1; the faintest five span 14.5$<$$T$$<$15.0.  The
fastest five have periods spanning 3.6\,hr$<$$P$$<$6.2\,hr, and the
slowest five span 27\,hr$<$$P$$<$38\,hr.  Regarding likely astrometric
or visual binaries, \ngoodhighruwe/\ngoods\ high-quality CQVs have a
Gaia DR3 RUWE$>$2; \nmaybehighruwe/\nmaybes\ of the ambiguous sample
share this characteristic.

@@

% IC\,2602 and IC\,2391, which are located slightly beyond 100\,pc, are
% an example of this completeness effect: our search did not find any
% CQVs in those clusters.

@@

As is typical for CQVs \citep{2017AJ....153..152S}, most CQVs in our
catalog did not show infrared excesses in the WISE1-4 bands.  Visually
inspecting the SEDs of our entire \ncpvsfound\ star sample, we labeled
two objects as having ``good'' infrared excesses (both W3 and W4 at
$>$3$\sigma$ above the photospheric prediction), and three as
``possible'' infrared excess (only W3 at $>$3$\sigma$).

The two ``good'' IR excesses belonged to ``ambiguous'' CQVs
TIC~193136669 (TWA~34) and TIC~57830249 (TWA~33).  Both are in the TW
Hydrae association ($\approx$10\,Myr), and have relatively long
periods of 38\,hr and 44\,hr respectively.  In our initial labeling,
we labeled both as ``ambiguous'' CQVs because the dips in their light
curves did not show the rigid periodicity typical of CQVs;  their
periods were also relatively long.  After labeling them, inspection of
further sectors clarified that both sources are dippers (see online
plots in Figure~\ref{fig:vet}).  Independently, TIC 193136669 has a
cold molecular disk based on observed 1.3\,mm continuum emission and
resolved Keplerian $^{12}{\rm CO}(2-1)$ emission
\citep{2015A&A...582L...5R}.  It was also labeled a dipper by
\citet{2022ApJS..263...14C}; we agree with their designation, but
nonetheless leave it in our catalog as an indication of possible
ambiguities in our search process.  TIC 57830249 (TWA~33) also has
previously detected 1.3\,mm continuum emission
\citep{2015A&A...582L...5R}, suggestive of cold dust grains being
present.  It is also a dipper.  Section~\ref{subsec:discdippers}
highlights plausible evolutionary connections between CQVs and dippers
in light of these ``misclassifications'' .

@@

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f10a.pdf}
			\includegraphics[width=0.48\textwidth]{f10b.pdf}
		}
	   \vspace{-0.1cm}

		\subfloat{
			\includegraphics[width=0.48\textwidth]{f10d.pdf}
			\includegraphics[width=0.48\textwidth]{f10c.pdf}
		}
	\end{center}
	\vspace{-0.4cm}
	\caption{
		{\bf River plots of the LP 12-502 light curve}, showing (clockwise from top-left)
		Sectors 18-19, 25-26, 53, and 58-59.  A two-harmonic sinusoid has
		been subtracted to highlight the sharp dips.
		In Sectors 25-26 (cycles 248-315), periods are visible at the fundamental
		period of 18.5611\,hr, as well as at faster and slower relative periods (e.g. $\phi$$\approx$0.3 and $\phi$$\approx$0.1).
		Similar instances of multiple simultaneous periods are also visible in
		Sector 53 and 58-59.
%		$P$=18.5611\,hr (gray vertical line); 18.5404\,hr (orange); 18.5683\,hr (green).
%		For Sector 53, gray is identical, while cyan is 18.5145\,hr.
%		For Sectors 58-59, the magenta line is 18.5473\,hr, and the green
%		line is 18.5672\,hr.
		White chunks denote missing data.
	}
	\label{fig:lpriver0}
\end{figure*}

Out of the \ngoods\ CQVs, a small fraction were in regions of sky with
many sectors of adjacent TESS data.  Out of these objects, LP 12-502
(TIC 402980664; $d$=21\,pc, $J$=9.4, $T$=11.1) stood out due to the
quality and content of its data.  We describe another interesting
source, TIC~300651846, in Appendix~\ref{app:tic3006}.  For this
section, we first present the LP 12-502 observations
(Section~\ref{subsec:lpobservations}), and then highlight their
interpretation (Section~\ref{subsec:lplessons}).

@@

The average period, determined by measuring the PDM peak period over
each sector independently, was $\langle P \rangle = 18.5560$\,hr.  The
range between the maximum and minimum sector-specific periods was
measured to be about one minute.   However, in detail, a period shift
of $\pm$1\,minute would yield major phase drifts over the baseline;
that time interval corresponds to $\approx$1/1000$^{\rm th}$ of a
period, and we have observed 1500 cycles.  By fine-tuning
over a grid in period, we eventually found $P=18.5611 \pm 0.0001$\,hr,
which seems to track certain features in the LP 12-502 light curve
well over the entire dataset.

@@

{\sc Dip durations}---The shortest dip duration for any of the
individual LP 12-502 dips seems to be $\approx$0.06\,$P$ $\approx$
1.08\,hr.  In comparison, using the stellar radius and mass derived in
Section~\ref{subsec:starprops}, the characteristic timescale $T_{\rm
dur} \equiv R_\star P / (\pi a)$ for the transit of a point-source at
corotation is 1.03\,hr ({\bf uncertainties?}).  This means that while
some of the LP 12-502 dips are sufficiently long to require structures
that are extended in orbital azimuth, the durations of other dips are
consistent with effective radii for the occulting material $R_{\rm
eff} \ll R_\star$.  This implies $a/R_\star \approx 5.8$ for this
material, and so the analogous timescale at the stellar surface is
about six times slower.

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.9\textwidth]{f7.pdf}
		\vspace{-0.1cm}
		\caption{
      {\bf Properties of CQVs identified by our search}.
      CQVs are mostly pre-main-sequence M dwarfs, younger than
      $\approx$150 Myr, with rotation periods faster than
      $\approx$1\,day.  The \ngoods\ bonafide CQVs in
      Table~\ref{tab:thetable} are the dark blue circles; \nmaybes\
      ambiguous CQV candidates are light blue circles.  The top panels
      show the \nstarssearched\ target stars with 120-second cadence
      TESS data as the shaded gray background; darker regions
      correspond to a larger relative number of searched stars.  The
      lower-left panel compares the rotation--color distribution of
      CQVs against the rotation periods of K and M dwarfs in the
      Pleiades from \citet{2016AJ....152..114R}.  The lower-middle
      panel plots the derived corotation radii $R_{\rm cr} =
      (GM/\Omega^2)^{1/3}$ in units of stellar radii against the
      measured CQV periods, in units of hours.  Ages in the final
      panel are known from cluster membership.
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}

@@

Figure~\ref{fig:catalogscatter} shows some of the derived stellar properties
for our CQV catalog, and compares them against both the target star
sample (top panels), and against stars in the Pleiades
\citep{2016AJ....152..114R}.  Typical CQV masses span
0.1-0.4\,$M_\odot$, and typical ages span 2-150\,Myr.  This is mass
and age includes both fully convective stars
($M_\star$$\lesssim$0.25\,$M_\odot$), and stars with a combination of radiative
cores and convective envelopes ($M_\star$$\gtrsim$0.25\,$M_\odot$;
\citealt{2018A&A...619A.177B}).  We found no obvious morphology
differences between the two classes, which is somewhat surprising 
if the two stellar classes tend to have distinct field topologies
\citep{2009A&A...496..787R}.  In terms of their rotation rates,
relative to the Pleiades, the CQVs are among the more rapidly rotating
half of M dwarfs.  The dearth of $T$$>$15.5 CQVs in our sample,
despite our search extending to $T$$=$16, is a consequence of the
120-second selection function, not detection sensitivity.

@@

The lowest mass ($\approx 0.12$\,$M_\odot$) belongs to TIC~267953787.
The catalog contains a few other stars with similar mass.  Given the
small number of sub-stellar mass objects in our target sample, future
studies of brown dwarf photometric variability might also yield CQVs,
though there could be degeneracies in interpretation with planetary
surface features such as clouds and latitudinal bands
\citep[e.g.][]{2021ApJ...906...64A,2022ApJ...924...68V}.

The two most massive CQVs in our sample might represent an interesting
new regime, but both have ambiguities.  To date, the only stars
reported to show the CQV phenomenon are M dwarfs, with typical stellar
masses $\lesssim$0.3\,$M_\odot$
\citep{2017AJ....153..152S,2022AJ....163..144G}.  TIC~405754448 and
TIC~405910546 however appear to have masses of $\approx$0.82\,$M_\odot$ and
$\approx$0.60\,$M_\odot$ respectively.  The next-highest masses in our
sample are $\approx$0.40\,$M_\odot$.  The masses for the former two
objects are consistent with their locations in the color--absolute
magnitude diagram, and with their membership in LCC.  However based on
its light curve morphology, TIC~405910546 should be studied in greater
depth, to confirm it is not an eclipsing binary.  For TIC~405754448,
we expect that the source is an unresolved binary, because RUWE$_{\rm
DR3}$=4.7, and because the raw light curves in Sectors 11, 37, and 38
for this source show an additional $\approx$6.5\,day, $\approx$0.3\%
amplitude sinusoidal signal suggestive of an unresolved photometric
companion.  If TIC~405754448 is a K+M binary, then the flux ratio
between the primary and secondary would be expected to be
$\approx$10:1.  It would be somewhat challenging for the M dwarf to
produce the observed 12.9\,hr signal with such a flux deficit, but not
impossible.  Therefore while both of these objects seem to suggest
that the CQV phenomenon may extend up in mass to pre-main-sequence K
dwarfs, more data are needed to fully substantiate this claim.

\subsection{TIC~425937691}

TIC~425937691 is a surprising case: it shows two seemingly independent
CQV signals on what appears to be the same star.  The two signals have
periods of $\approx$4.82\,hr and $\approx$3.22\,hr, respectively.
The former is the larger amplitude signal visible in
Figures~\ref{fig:cqvs} and~\ref{fig:evoln}, corresponding to signal
with peak-to-peak amplitude of $\approx$8\%.  The latter signal is
only visible after subtracting the primary period, and it has a
sinusoidal envelope with a peak-to-peak amplitude of 2.5\%, and with
three sharp dips super-posed over each cycle.  For
TIC~425937691, ${\rm RUWE}_{\rm DR3}=2.9$.

The explanation that seems most likely for this source, given the two
photometric signals and the elevated RUWE, is an unresolved binary
consisting of two CQVs.  Recent work has shown that the orbits of
binaries closer than $\lesssim$700 AU tend to be aligned with their
planetary systems \citep{2022AJ....163..207C}.  If we assume that
observing CQV variability similarly requires near edge-on viewing
geometries, then we might expect a sufficiently close binary with one
CQV to also have another, since the spin axes in sufficiently close
binaries would tend to be aligned.  In this scenario, the two periods
being within $\approx$0.2\% of the 3:2 period commensurability would
simply be a coincidence.

\subsection{TIC~435903839}

%TODO: move these to their own ``debunked'' table, I think...
%TODO: along with the IR excess ones

TIC~435903839, which we originally classified as an ``ambiguous'' CQV,
is an apparently similar case.  We initially labeled this source as
having a 10.82\,hr period, because this period minimized the
dispersion in the phase-folded light curve.  However closer inspection
reveals that this source is a photometric blend of two ordinary
rotating stars with $P_0$=3.60\,hr, and $P_1$=5.41\,hr.  This is a
novel false positive scenario for CQVs: two rapidly-rotating stars
with near-integer ratios of rotation periods.  The beat between the
two rotation signals produces the spurious CQV signal.  Such false
positives can be excluded through careful accounting of all peaks in a
periodogram.  For instance, TIC~435903839 shows a peak at 16.27\,hr,
which is not an integer multiple of the nominal ``10.82\,hr'' period.

@@

\begin{figure}[!th]
	\begin{center}
		\centering
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f8a.pdf}
		}

		\vspace{-0.4cm}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f8b.pdf}
		}

>>>>

The CQV light curves cannot be explained by pure starspots.  Although
all young M dwarfs are spotted, this tends to produce flux variations
over characteristic timescales of the rotation period, $P_{\rm rot}$,
and its half-harmonic, $0.5\,P_{\rm rot}$.  If one fine-tunes the
viewing geometry, starspots can produce dips with durations as short
as $\approx$$0.2\,P_{\rm rot}$, and the dip amplitudes quickly
decrease due to limb-darkening (see \citealt{2017AJ....153..152S},
Figures 37-41).  The observed dips can happen over durations as
short as $0.05\,P_{\rm rot}$ with characteristic depths of a few
percent; a ``starspot-only'' scenario can be discarded for any object
with dips that are sufficiently deep and short in duration
\citep{2017AJ....153..152S,2021MNRAS.500.1366K}.   The timescales and
amplitudes of the flux variations in such objects instead require
sharp geometries with material extrinsic to the stellar surface
\citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  Since the
CQVs are probably all explained by the same phenomenon, we
therefore discard the ``spot-only'' scenario.

A few competing explanations for what causes the complex quasiperiodic
variability are shown in Figure~\ref{fig:f1}.  The ``clump'' scenario
invokes opaque dust clumps periodically transiting the star near the Keplerian corotation
radius, $R_{\rm cr} = (GM/\Omega^2)^{1/3}$
\citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  The ``prominence''
scenario invokes long-lived condensations of cool and dense
marginally-ionized gas, embedded within the hotter corona, that would
be centrifugally supported to also be near corotation
\citep{1989MNRAS.238..657C,2019MNRAS.482.2853J,2022MNRAS.514.5465W}.
Such structures are analogous to quiescent prominences and filaments
seen in the solar corona \citep[see e.g.][]{2015ASSL..415.....V},
though at much larger relative distances from the stellar surface.  A
final possibility is one of a ``screen'', in
which the inner wall of a quiescent circumstellar disk blocks a
portion of the stellar surface to produce sudden dips whenever spots
come into view \citep{2019ApJ...876..127Z}.

The dust clump and prominence hypotheses seem most plausible.  They
are qualitatively similar, except that one invokes opacity from dust,
while the other invokes opacity from gas, likely bound-free
transitions in hydrogen or perhaps a molecular opacity.  The screen
scenario seems inconsistent with the sharpness
of the observed dips,
the lack of infrared excess, and the observed lifetime of CQVs
extending an order of magnitude longer than the $\approx$$10^7$ year
timescale often quoted for primordial disk dispersal.  However,
unambiguous evidence in support of any one scenario has yet to be
acquired.  Such evidence might include a spectroscopic detection of
silicate 10\,$\mu$m dust absorption during a dip, or perhaps detection
of transient Balmer-line excesses as a function of cycle phase,
similar to observations made in systems such as AB~Dor
\citep[see][]{1999ASPC..158..146C} or PTFO 8-8695
\citep{2016ApJ...830...15J}.

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.96\textwidth]{f2.pdf}
		\vspace{-0.3cm}
		\caption{
			{\bf Validation plots used to  label CQVs}.  The complete figure
			set, with one image per sector for each of \ncpvsfound\ CQVs
			and CQV candidates
			is available online {\bf For internal collaboration review:
				\url{https://www.dropbox.com/scl/fo/zlj3txot4cvymfb22wewu/h?dl=0&rlkey=3ec5f9o5xewrixzfkhkdenopa}}.
			Panels are as follows.
			{\it a)}: Phase-folded light curve; gray points are raw 2-minute
			data and black points are binned to 200 points per cycle.
			{\it b)}: Phase-dispersion minimization (PDM) periodogram.
			Dotted lines show up to the 10$^{\rm th}$ harmonic and
			subharmonic.
			{\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
			circles displayed for scale.
			{\it d)}: Cleaned light curve, binned to 20-minute cadence, in
			Barycentric TESS Julian Date (BTJD).
			{\it e)}: Phase-folded light curve, binned to 100 points per
			cycle.  The gray line denotes the automated spline-fit to the
			wrapped phase-folded light curve, and small gray triangles
			denote automatically identified local minima.
			{\it f)}: Phase-folded light curve at twice the peak period.
			{\it g)}: Phase-folded light curve at half the peak period.
			{\it h)}: Phase-folded time-series within the ``background''
			aperture defined in the SPOC light curves.
			{\it i)}: Phase-folded flux-weighted centroid in the column
			direction.
			{\it j)}: Phase-folded flux-weighted centroid in the row
			direction.
			{\it k)}: Gaia DR2 color--absolute magnitude diagram.     
			The gray background denotes stars within 100\,pc.
			{\it l)}: Information from Gaia DR2, TIC8, and the automated
			dip-counting search pipeline.  ``Neighbors'', abbreviated
			``nbhr'', are listed within apparent distances of 2 TESS pixels
			if $\Delta T$$<$2.5.
			{\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities, calculated
			using positions, proper motions, and the parallax.
		}
		\label{fig:vet}
	\end{center}
\end{figure*}

@@

The mosaic in Figure~\ref{fig:cqvs} shows phased light curves for the
\ngoods\ CQVs.  The objects are sorted first in order of the number of
TESS 120-second cadence sectors in which they clearly demonstrated the
CQV phenomenon, and secondarily by descending brightness.  The top
five objects by this metric are TIC~300651846 ($T$$=$13.5, 12
sectors); TIC~402980664 ($T$$=$11.1, 7 sectors); TIC~89463560
($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5 sectors); and
TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest five CQVs span
9.3$<$$T$$<$11.1; the faintest five span 14.5$<$$T$$<$15.0.  The
fastest five have periods spanning 3.6\,hr$<$$P$$<$6.2\,hr, and the
slowest five span 27\,hr$<$$P$$<$38\,hr.  Regarding likely astrometric
or visual binaries, \ngoodhighruwe/\ngoods\ high-quality CQVs have a
Gaia DR2 RUWE$>$2; \nmaybehighruwe/\nmaybes\ of the ambiguous sample
share this characteristic.

@@

@@

Most CQVs in our catalog did not show infrared excesses in the W1-W4
bands, which is typical for this class of object
\citep{2017AJ....153..152S}.  Visually inspecting the SEDs of our
\ncpvsfound\ star sample, we labeled two objects as having ``good''
infrared excesses (both W3 and W4 at $>$3$\sigma$ above the
photospheric prediction), and three as ``possible'' infrared excess
(only W3 at $>$3$\sigma$).

The two ``good'' IR excesses belonged to TIC~193136669 (TWA~34) and
TIC~57830249 (TWA~33).  Both are in the TW Hydrae association
($\approx$10\,Myr), and have relatively long periods of 38\,hr and
44\,hr respectively.  In our initial labeling, we labeled both as
``ambiguous'' CQVs because the dips in their light curves did not show
the rigid periodicity typical of CQVs;  their periods were also
relatively long.  However, inspection of further sectors clarified
that both sources are dippers (see online plots in
Figure~\ref{fig:vet}).  Independently, TIC 193136669 has a cold
molecular disk based on observed 1.3\,mm continuum emission and
resolved Keplerian $^{12}{\rm CO}(2-1)$ emission
\citep{2015A&A...582L...5R}.  It was also labeled a dipper by
\citet{2022ApJS..263...14C}; we agree with their designation, and
label it an ``impostor'' CQV in Table~\ref{tab:thetable}.  TIC
57830249 (TWA~33) also has previously detected 1.3\,mm continuum
emission \citep{2015A&A...582L...5R}, suggestive of cold dust grains
being present.  It is also a dipper.  Section~\ref{subsec:discdippers}
highlights plausible evolutionary connections between CQVs and dippers
in light of these ``misclassifications'' .

@@

\begin{figure*}[!tp]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f7a.pdf}
			\includegraphics[width=0.48\textwidth]{f7b.pdf}
		}
	   \vspace{-0.1cm}

		\subfloat{
			\includegraphics[width=0.48\textwidth]{f7d.pdf}
			\includegraphics[width=0.48\textwidth]{f7c.pdf}
		}
	\end{center}
	\vspace{-0.4cm}
	\caption{
    {\bf River plots of the LP 12-502 light curve}, showing (clockwise
    from top-left) Sectors 18-19, 25-26, 53, and 58-59.  A
    two-harmonic sinusoid has been subtracted to highlight the sharp
    dips.  In Sectors 25-26 (cycles 248-315), periods are visible at
    the fundamental period of 18.5611\,hr, as well as at faster and
    slower relative periods (e.g. $\phi$$\approx$0.3 and
    $\phi$$\approx$0.1).  Similar instances of multiple simultaneous
    periods are also visible in Sector 53 and 58-59.  White chunks
    denote missing data.
	}
	\label{fig:lpriver0}
\end{figure*}

Out of the \ngoods\ CQVs, a small fraction were in regions of sky with
many sectors of adjacent TESS data.  Out of these objects, LP 12-502
(TIC 402980664; $d$=21\,pc, $J$=9.4, $T$=11.1) stood out due to the
quality and content of its data.  We describe another interesting
source, TIC~300651846, in Appendix~\ref{app:tic3006}.  In this
section, we first present the LP 12-502 observations
(Section~\ref{subsec:lpobservations}), and then highlight their
implications (Section~\ref{subsec:lplessons}).

@@

The average period, determined by measuring the PDM peak period over
each sector independently, was $\langle P \rangle = 18.5560$\,hr.  The
range between the maximum and minimum sector-specific periods was
measured to be about one minute.   However, in detail, a period shift
of $\pm$1\,minute would yield major phase drifts over the baseline;
that time interval corresponds to $\approx$1/1000$^{\rm th}$ of a
period, and we have observed 1500 cycles.  By fine-tuning over a grid
in period, we found $P=18.5611 \pm 0.0001$\,hr, which seems to track
certain features in the LP 12-502 light curve well over the entire
dataset.

@@

{\sc Dip durations}---The shortest dip duration for any of the
individual LP 12-502 dips seems to be $\approx$0.06\,$P$ $\approx$
1.08\,hr.  In comparison, using the stellar radius and mass derived in
Section~\ref{subsec:starprops}, the characteristic timescale $T_{\rm
dur} \equiv R_\star P / (\pi a)$ for the transit of a point-source at
corotation is 1.02$\pm$0.10\,hr.  This means that while
some of the LP 12-502 dips are sufficiently long to require structures
that are extended in orbital azimuth, the durations of other dips are
consistent with effective radii for the occulting material $R_{\rm
eff} \ll R_\star$.  This implies $a/R_\star \approx 5.8$ for this
material; the analogous timescale at the stellar surface is
about six times slower.

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.95\textwidth]{f8.pdf}
		\vspace{-0.1cm}
		\caption{
      {\bf Properties of CQVs identified by our search}.
      CQVs are mostly pre-main-sequence M dwarfs, younger than
      $\approx$150 Myr, with rotation periods faster than
      $\approx$1\,day.  The \ngoods\ bonafide CQVs in
      Table~\ref{tab:thetable} are the dark blue circles; \nmaybes\
      ambiguous CQV candidates are light blue circles.  Cases with
      elevated Gaia DR2 RUWE values are highlighted.
      The top panels show the \nstarssearched\ target stars with
      120-second cadence TESS data as the shaded gray background;
      darker regions correspond to a larger relative number of
      searched stars.  The lower-left panel compares the
      rotation--color distribution of CQVs against the rotation
      periods of K and M dwarfs in the Pleiades from
      \citet{2016AJ....152..114R}.  The lower-middle panel plots the
      derived corotation radii $R_{\rm cr} = (GM/\Omega^2)^{1/3}$ in
      units of stellar radii against the measured CQV periods, in
      units of hours.  Ages in the final panel are known from cluster
      membership.
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}

@@

Figure~\ref{fig:catalogscatter} shows derived stellar
properties for our CQV catalog, and compares the CQVs against both the
target star sample (top panels), and against stars in the Pleiades
\citep{2016AJ....152..114R}.  Typical CQV masses span
0.1-0.4\,$M_\odot$, and typical ages span 2-150\,Myr.  This mass
and age range includes both fully convective stars
($M_\star$$\lesssim$0.25\,$M_\odot$), and stars with a combination of
radiative cores and convective envelopes
($M_\star$$\gtrsim$0.25\,$M_\odot$; \citealt{2018A&A...619A.177B}).
We found no obvious morphology differences between the two classes,
which is somewhat surprising given that the star's interior structure may influence
the field topology \citep{2009A&A...496..787R}.  In terms of
their rotation rates relative to the Pleiades, the CQVs are among the
more rapidly rotating half of M dwarfs. 
%The dearth of $T$$>$15.5 CQVs
in our sample, despite our search extending to $T$$=$16, is a
consequence of the 120-second selection function, not detection
sensitivity.

@@

The lowest mass ($\approx$$0.12$\,$M_\odot$) belongs to TIC~267953787.
The catalog contains a few other stars with similar mass.  Given the
small number of sub-stellar mass objects in our target sample, future
studies of brown dwarf photometric variability might also yield CQVs,
though there could be degeneracies in interpretation with planetary
surface features such as clouds and latitudinal bands
\citep[e.g.][]{2021ApJ...906...64A,2022ApJ...924...68V}.

\subsection{Binaries, massive CQVs, and a new class of false positive}

The high-RUWE objects in Figure~\ref{fig:catalogscatter} tend to be
among the more massive half of the CQV sample.  This suggests that either
that the RUWE indicator is not sensitive to binarity among lower mass
stars, or that these ``high-mass CQVs'' may be unresolved blends in
which the lower mass companion is produces the CQV signal.

\subsubsection{Do K dwarf CQVs exist?}
\label{subsec:massive}

The two most massive CQVs in our sample present a relevant case study.
To date, the only stars reported to show the CQV phenomenon are M
dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
\citep{2017AJ....153..152S,2022AJ....163..144G}.  TIC~405754448 and
TIC~405910546 however appear to have masses of
$\approx$0.82\,$M_\odot$ and $\approx$0.60\,$M_\odot$ respectively.
The next-highest masses in our sample are $\approx$0.40\,$M_\odot$.
The masses for the former two objects are consistent with their
locations in the color--absolute magnitude diagram, and with their
membership in LCC.  However the light curve morphology of
TIC~405910546 is unique among the CQV sample, and suggestive of an
eclipsing binary; it should be studied further to clarify its
classification.  For TIC~405754448, we expect that this source {\it
is} an unresolved binary, because RUWE$_{\rm DR2}$=4.7, and because
the raw light curves in Sectors 11, 37, and 38 show an
additional $\approx$6.5\,day, $\approx$0.3\% amplitude sinusoidal
signal suggestive of an unresolved photometric companion.  If
TIC~405754448 is a K+M binary, then the flux ratio between the primary
and secondary would be expected to be $\approx$10:1.  It would be
challenging for the M dwarf to produce the observed 12.9\,hr signal
with such a flux deficit, but not impossible.  While both of
these objects suggest that the CQV phenomenon may extend up in mass to
pre-main-sequence K dwarfs, more data are needed to fully substantiate
this claim.

\subsubsection{Systems near the 3:2 commensurability}

\paragraph{TIC~435903839}
We originally classified TIC~435903839, with RUWE$_{\rm DR2}$=11.6, as
an ``ambiguous'' CQV with 
a 10.82\,hr period, because this period minimized the
dispersion in the phase-folded light curve.  However careful inspection
of the periodogram
reveals that this source is a photometric blend of two ordinary
rotating stars with $P_0$=3.60\,hr, and $P_1$=5.41\,hr.  This is a
novel false positive scenario for CQVs: two rapidly-rotating stars
with near-integer ratios of rotation periods.  The beat between the
two rotation signals produces the apparent CQV signal.  Such false
positives can be excluded through careful accounting of all peaks in a
periodogram.  For instance, TIC~435903839 shows a peak at 16.27\,hr,
which is not an integer multiple of the dispersion-minimizing 10.82\,hr period.
This particular case is an ``impostor'' CQV.

\paragraph{TIC~425937691}
TIC~425937691 is an odd converse case: it shows two seemingly independent
CQV signals on what appears to be the same star.  The two signals have
periods of $\approx$4.82\,hr and $\approx$3.22\,hr, and so also fall near
the 3:2 commensurability.
The former is the larger amplitude signal visible in
Figures~\ref{fig:cqvs} and~\ref{fig:evoln}, corresponding to signal
with peak-to-peak amplitude of $\approx$8\%.  The latter signal is
only visible after subtracting the primary period, and it has a
sinusoidal envelope with a peak-to-peak amplitude of 2.5\%, and with
three sharp dips super-posed over each cycle.  For
TIC~425937691, ${\rm RUWE}_{\rm DR2}=2.9$.

Given the two photometric signals and the elevated RUWE, this source is 
probably an unresolved binary consisting of two CQVs.  Recent work has shown that the orbits of
binaries closer than $\lesssim$700 AU tend to be aligned with their
planetary systems \citep{2022AJ....163..207C}.  If we assume that
observing CQV variability similarly requires near edge-on viewing
geometries, then we might expect a sufficiently close binary with one
CQV to also have another, since the spin axes in sufficiently close
binaries would tend to be aligned.  In this scenario, the two periods
being within $\approx$0.2\% of the 3:2 period commensurability would
simply be a coincidence.

@@

\begin{figure}[!th]
	\begin{center}
		\centering
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f9a.pdf}
		}

		\vspace{-0.4cm}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f9b.pdf}
		}

		\vspace{-0.4cm}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f9c.pdf}
		}
